Factor Analysis on Citations, Using a Combined Latent and Logistic Regression Model

### 2019-09-09 Manuscript for submission/manuscript.tex
Update

\begin{remark}
Throughout the Section, we add $*$ to the superscript of parameters to denote that they are ground truth parameters.
We use $\alpha^*$ as an intercept term in logistic regression model, and
$f^*_j$ as $j$th column of factor loading matrix $F^* \in \mathbb{R}^{K \times n}$, where $K$ refers to the number of topics embedded in network, and $n$ denotes the number of papers in the network.
Here, we introduce another notation, $n_{l}$, denoting the number of papers, which share $l$ common topics.
Matrix $D^* \in \mathbb{R}^{K \times K}$ is a diagonal matrix whose entries denote weight coefficient of factors, and
$S_{ij}^*$ denotes an ad-hoc citational relation between $i$th and $j$th paper.
We use the notation $|S^*|$ to denote the cardinality of non-zero components of upper-triangular part of $S^*$ matrix
(i.e., $|S^*|=|\{(i,j) : S_{ij}^{*}\neq 0, 1 \leq i<j \leq n\}|$).
%We will use $X \sim \text{Unif}[a,b]$ to denote
%the random variable $X$ is drawn from uniform distribution supported on the interval $[a,b]$.
\end{remark}

\subsection{Numerical experiments with synthetic data}
\label{sec:Syn-dat}
After a brief introduction on several synthetic scenarios that we want to explore, we will discuss how to set ground truth parameters for generating synthetic networks from pre-specified scenarios.
Subsequently, three model selection criteria and three evaluation metrics for the selected model will be introduced.
Lastly, several interesting observations from the experiments will be presented.

\begin{figure}[htbp]
\includegraphics[width=1\textwidth]{Fig1.pdf}
\caption{Illustrations of assignment results via $k$-means algorithm on $K$ eigenvectors of the estimated $\widehat{L}$ matrix.}
\label{fig:figure1}
\end{figure}

\subsubsection{Synthetic Setting}
In this subsection, we consider $3$ scenarios.
In first scenario, we examine a simple setting, in which every paper in the network has only one topic.
In second scenario, we study a slightly more complicated situation than the first one where each paper in the network can possibly have more than one topic.
%It is worth noting that different clusters of papers, where each cluster is comprised of papers with same topic, are connected via ad-hoc links.

More concretely, in first scenario, when there is a network of $n$ papers with $K$ topics, there are $K$ clusters of papers, where each of which deals with $1$ specific topic out of $K$ topics.
And each cluster is comprised of $\frac{n}{K}$ non-overlapping papers.
Moreover, these $K$ clusters are connected with each other via $|S^*|$ random ad-hoc links.
Specifically, we assume $|S^*|/\binom{K}{2}$ ad-hoc links connect $2$ different clusters of papers.
For example, suppose that we have a network of $120$ papers with $5$ topics and with $30$ random ad-hoc links. Then, there are $5$ clusters, each of which has $24$ papers, and each of $10(=\binom{5}{2})$ pairs of clusters is connected through $3(=30/\binom{5}{2})$ random ad-hoc links.
%(See Fig$\ref{fig:figure1}$

Based upon the settings mentioned in the first scenario, additionally in second scenario, we suppose that there are $n_{l}$ papers, which share $l(\leq K)$ common topics in the network.
For instance, if we have a network of $210$ papers with $3$ topics, and
$n_2=50$, then $n_2=50$ means that there are $50$ papers out of $210$ papers, which have $2$ shared topics out of $3$ topics.
Here, we want to note the readers that ad-hoc links are not used either to connect the clusters of papers that share $l$ common topics, or to connect a cluster of $1$ topic and a cluster that share $l$ common topics.
In order to represent this notion in a generated network,
first, we randomly pick $n_{l}$ indices from the set $\Omega_{n_{l}} = \{1,2,\dots,n\} \setminus \Omega_{S^*}$, where $\Omega_{S^*}$ denotes a set of indices of papers for formulating $|S^*|$ ad-hoc links.
Next, $\forall j \in \Omega_{n_{l}}$, fill in arbitrary $l$ positions of $f_j^*$ with $1$s.

@@

\begin{enumerate}
    \item In the first scenario, we consider following three cases: $\{(n^{(i)},n_{1}^{(i)},K^{(i)},|S^*|^{(i)})\}_{i=1}^{3}$ $=\{(30,30,3,9), (80,80,4,18),$ $(120,120,5,30)\}$.
        If we take an example, the notation  $(n^{(1)},n_{1}^{(1)},K^{(1)},|S^*|^{(1)})=(30,30,3,9)$ means that we generate a network with $30$ papers. There are $3$ topics embedded in the network, and $9$ random ad-hoc links connect $3$ clusters of papers, where each cluster represents a collection of papers with same topic.
        Note that every paper in three networks, which are considered in this scenario, studies only about $1$ topic among $K$ topics.
    \item In the second scenario, we consider three cases where we have
        $\{(n^{(i)},n_{2}^{(i)},n_{3}^{(i)},K^{(i)},|S^{*}|^{(i)})\}_{i=1}^{3}=
        \{(120,0,10,3,18),$ $(210,50,0,3,18),(210,10,10,3,18)\}$.
        For instance, in the third case, we have a network with $210$ papers in total. There are $3$ topics commonly shared across the network.
        Among $210$ papers, $10$ papers randomly share $2$ topics out of $3$, other $10$ papers have $3$ mixed topics, whereas remaining $190$ papers only discuss $1$ topic.
        Note that $3$ clusters from these $190$ papers are connected through $18$ random ad-hoc links.
        % For all $3$ cases, networks considered in this scenario have $3$ topics, and $3$ clusters of papers are connected via $18$ random ad-hoc links.
        % In the first case, we generate a network with $120$ papers in total, which is comprised of $110$ papers with $1$ topic, and $10$ papers with $3$ mixed topics.
        % In the second case, we have a network with $210$ papers in total.
        % Among them, $50$ papers randomly share $2$ topics out of $3$ topics.
        % And remaining $160$ papers talk about only $1$ topic.
        % Lastly, in the third case, the network to be considered has $210$ papers in total.
        % Among them, $10$ papers randomly share $2$ topics out of $3$, other $10$ papers have $3$ mixed topics, whereas remaining $190$ papers only discuss $1$ topic.
    \item adsfasdf
\end{enumerate}

All $9$ networks that are elaborated in scenarios $1$, $2$ and $3$ are visualized in Fig\ref{fig:figure1}.
Note that ad-hoc links, which connect clusters of papers with $1$ topic, are colored in green.
For more detailed descriptions on parametric settings for generating networks in Fig\ref{fig:figure1}, readers can refer the R code provided in $\dots$.
%In next subsection, we provide detailed ground truth parameters settings for generating the networks in Fig\ref{fig:figure1}.

@@

\subsubsection{Choosing the tuning parameters and evaluation criteria}

We observe that choosing a good pair of tuning parameters is an important yet challenging issue in our setting.
Here we present a heuristic approach.
Following the approach in Ji and Jin \cite{ji2016coauthorship}, we plot the largest $20$ eigenvalues of adjacency matrix $X$, which can tell us the number of communities embedded in the network
(See Fig\ref{fig:figure2} to check for the cases of $6$ aforementioned synthetic networks).
Then, we record the rank of $\widehat{L}$ and number of non-zero elements in $\widehat{S}$ for each tuning parameter pair on a given grid, and choose a proper pair that gives us interesting interpretations of data.

One might wonder how traditional model selection methods, such as the Bayes Information Criterion (BIC;\cite{schwarz1978estimating}) and the AIC, work where we recall that BIC and AIC are defined as follows:
\[
\mbox{BIC}(M) = -2  \mathbb{L}_n( \hat{\beta}(M)) + |M| \log \bigg(\frac{n(n-1)}{2}\bigg),
\]
and
\[
\mbox{AIC}(M) = -2  \mathbb{L}_n( \hat{\beta}(M)) + 2|M|,
\]
where $M$ is the current model,
$\mathbb{L}_n( \hat{\beta}(M))$ is the maximal log-likelihood for a given model $M$,
and $|M|$ is the number of free parameters in $M$, which is determined by the number of non-zeros in $S$ and the low-rank matrix $L$.
If we have $\text{rank}(L)=K$, we can establish the following
\[
|M| = \sum_{i < j}1_{\{S_{ij} > 0\}} + n K - \frac{K(K-1)}{2} + 1 ;
\]
since the number of free parameters in $L$ is $K$ plus $nk - K(K+1)/2$, which is the number of free parameters in determining $K$ orth-normal vectors.
Additionally $1$ in the last is due to $\alpha$.
We want to find an $M$, which minimizes BIC($M$) or AIC($M$) as a function of $M$.
However these traditional methods seem to entail a serious problem.
%The assumptions used to derive BIC or AIC are not satisfied here, since each edges in a graph are not identically distributed.
Our experience shows that both BIC and AIC choose the most parsimonious model with the smallest $K(=\text{rank}(\widehat{L}))$ and the smallest cardinality$(=|\widehat{S}|)$ of ad-hoc links among all the estimated ($\widehat{L}$,$\widehat{S}$)s' over the given grid.
We evaluate the models that are selected via our heuristic approach, BIC, and AIC by using following three evaluation metrics.

\begin{figure}[htbp]
\includegraphics[width=1\textwidth]{Fig2.pdf}
\caption{\it Scree plots. From left to right: 543-Citation network, Mixed Topics-Citation network.}
\label{fig:figure2}
\end{figure}

@@

\subsubsection{Several Observations}
Given a network data $X$, after fitting the model with a proper pair of tuning parameters, $(\gamma,\delta)$, we need to determine whether node $i$ belongs to $k$th topic or not.
We applied a simple $k$-means clustering on the fitted $L$ matrix's $K$ eigenvectors.
For the illustration of performance of our fitted model after applying $k$-means algorithm on three synthetic scenarios, in Fig\ref{fig:figure1}, we plot the coordinates of each rows of first two eigen-vectors on $2$D plane.
%Furthermore, we find one interesting phenomenon.
%Coordinates of each rows from first two eigenvectors of estimated $\widehat{L}$ matrix in our model characterize the clustering behavior of embedded topics reasonably well.
%Our experience shows that with only first two eigenvectors of $\widehat{L}$, we can also cluster the nodes comparably well.

\textbf{Ad-hoc links}.
Ad-hoc links of synthetic network data can be thought of as ``across edges'' between clusters of nodes.
Since indices of non-zero entries of $S^{*}$ are randomly chosen, there might be some indices of positive $S^{*}_{ij}$ entries where $L^{*}_{ij}$ is also positive.
In this case, this makes the edges indistinguishable if they come from $S^{*}_{ij}$ or $L^{*}_{ij}$.
%Some of ``across edges" are also attributed to $\alpha^{*}$, and unfortunately, our algorithm cannot make a difference whether the edge comes from $\alpha^{*}$ or $S^{*}_{ij}$.
So the total number of ``across edges'' might not be exactly same as $|S^*|$ as we set in our data generation setting.

@@

\centering
\begin{tabular}{c|ccc|ccc|ccc}
            & \multicolumn{9}{c}{\textbf{Scenario 1}}                                              \\
            \cline{2-10}
            & \multicolumn{3}{c|}{Case 1} & \multicolumn{3}{c|}{Case 2} & \multicolumn{3}{c}{Case 3} \\
            \cline{2-10}
            & Heuristic   & AIC   & BIC  & Heuristic   & AIC   & BIC  & Heuristic   & AIC   & BIC  \\
            \hline
$M_{1}$          &             &       &      &             &       &      &             &       &      \\
$M_{2}$          &             &       &      &             &       &      &             &       &      \\
$M_{3}$          &             &       &      &             &       &      &             &       &      \\
Grid Region &    &       &      &             &       &      &             &       &      \\
            \hline
\end{tabular}

\begin{tabular}{c|ccc|ccc|ccc}
            & \multicolumn{9}{c}{\textbf{Scenario 2}}                                              \\
            \cline{2-10}
            & \multicolumn{3}{c|}{Case 4} & \multicolumn{3}{c|}{Case 5} & \multicolumn{3}{c}{Case 6} \\
            \cline{2-10}
            & Heuristic   & AIC   & BIC  & Heuristic   & AIC   & BIC  & Heuristic   & AIC   & BIC  \\
            \hline
$M_{1}$          &             &       &      &             &       &      &             &       &      \\
$M_{2}$        &             &       &      &             &       &      &             &       &      \\
$M_{3}$       &             &       &      &             &       &      &             &       &  \\
Grid Region &             &       &      &             &       &      &             &       &      \\
\end{tabular}

\begin{tabular}{c|ccc|ccc|ccc}
            & \multicolumn{9}{c}{\textbf{Scenario 3}}                                              \\
            \cline{2-10}
            & \multicolumn{3}{c|}{Case 7} & \multicolumn{3}{c|}{Case 8} & \multicolumn{3}{c}{Case 9} \\
            \cline{2-10}
            & Heuristic   & AIC   & BIC  & Heuristic   & AIC   & BIC  & Heuristic   & AIC   & BIC  \\
            \hline
$M_{1}$          &             &       &      &             &       &      &             &       &      \\
$M_{2}$        &             &       &      &             &       &      &             &       &      \\
$M_{3}$       &             &       &      &             &       &      &             &       &  \\
Grid Region &             &       &      &             &       &      &             &       &      \\
\end{tabular}

\caption{ For three scenarios, our heuristic method chooses the model with $\widehat{L}$ with true rank, $\widehat{S}$ whose $M_2$ value is close to $1$, and $M_3$ value is close to $0$.
Note that, for all three scenarios, both AIC and BIC choose the model with no ad-hoc structure (i.e., $\widehat{S}=0$), and $\widehat{L}$ with rank $1$ (i.e.,$\text{rank}(\widehat{L})=1$).}
\label{tab:table1}
\end{table}

\begin{figure}[htbp]
\includegraphics[width=1\textwidth]{Fig3.pdf}
\caption{\it Scree plots. From left to right: 543-Citation network, Mixed Topics-Citation network.}
\label{fig:figure3}
\end{figure}

@@

\noindent These two topics are classical research topics in field of statistics.
First group talks about Variable Selection in high-dimensional data.
Majority of papers in second community study about Controlling False Discovery Rate in various statistical settings.
As expected, third group is quite hard to interpret and seems to have substructures.
For further investigation on this group, after obtaining the sub-network which is comprised only with the papers in the third group, we performed same analysis once again under the assumption that $K=4$ (See $Fig \ref{fig:figure3},right$).
We obtain four sub-communities as follows:

>>>>

\begin{remark}
Throughout the Section, we add $*$ to the superscript of parameters to denote that they are ground truth parameters.
We use $\alpha^*$ as an intercept term in logistic regression model, and
$f^*_j$ as $j$th column of factor loading matrix $F^* \in \mathbb{R}^{K \times n}$, where $K$ refers to the number of topics embedded in network, and $n$ denotes the number of papers in the network.
We also introduce a notation, $n_{l}$, denoting the number of papers, which share $l$ common topics.
Matrix $D^* \in \mathbb{R}^{K \times K}$ is a diagonal matrix whose entries denote weight coefficient of factors, and
$S_{ij}^*$ denotes an ad-hoc citational relation between $i$th and $j$th paper.
We use the notation $|(\bullet)|$ to denote the cardinality of non-zero components of upper-triangular part of $(\bullet)$ matrix
(e.g., $|S^*|=|\{(i,j) : S_{ij}^{*}\neq 0, 1 \leq i<j \leq n\}|$).
We will use $X \sim \text{Unif}[a,b]$ to denote
the random variable $X$ is drawn from uniform distribution supported on the interval $[a,b]$.
\end{remark}

\subsection{Numerical experiments with synthetic data}
\label{sec:Syn-dat}
After an introduction on three synthetic scenarios that we want to explore, three model selection criteria and three evaluation metrics for the selected model will be suggested.
Experimental results from the synthetic networks and several interesting findings from those results will be elaborated subsequently.

\begin{figure}[htbp]
\includegraphics[width=1\textwidth]{Fig1.pdf}
\caption{Graphical illustrations of $9$ synthetic networks. Note the links that are drawn from $S^*_{ij} \neq 0$ are colored in green. }
\label{fig:figure1}
\end{figure}

\subsubsection{Synthetic Setting}
In this subsection, we consider following $3$ scenarios:
%In this subsection, we consider $3$ scenarios.
%In first scenario, we examine a simple setting, in which every paper in the network has only one topic.
%In second scenario, we study a more complicated situation than the first one where each paper in the network can possibly have more than one topic.
%It is worth noting that different clusters of papers, where each cluster is comprised of papers with same topic, are connected via ad-hoc links.
%In third scenario, we consider a situation
\begin{itemize}
    \item \textbf{First scenario.} When there is a network of $n$ papers with $K$ topics, there are $K$ clusters of papers, where each of which deals with $1$ specific topic out of $K$ topics.
        And each cluster is comprised of $\frac{n}{K}$ non-overlapping papers.
        Moreover, these $K$ clusters are connected with each other via $|S^*|$ random ad-hoc links.
        Specifically, we assume $|S^*|/\binom{K}{2}$ ad-hoc links connect $2$ different clusters of papers.
        For example, suppose that we have a network of $120$ papers with $5$ topics and with $30$ random ad-hoc links. Then, there are $5$ clusters, each of which has $24$ papers, and each of $10 (=\binom{5}{2})$ pairs of clusters is connected through $3 (=30/\binom{5}{2})$ random ad-hoc links.
%(See Fig$\ref{fig:figure1}$

    \item \textbf{Second scenario.} Based upon the settings mentioned in the first scenario, we suppose that there are $n_{l}$ papers, which share $l(\leq K)$ common topics in the network.
        For instance, if we have a network of $210$ papers with $3$ topics, and
        $n_2$ is equal to $50$, then this means that there are $50$ papers out of $210$ papers, which have $2$ shared topics out of $3$ topics.
        %Here, we want to note the readers that ad-hoc links are not used either to connect the clusters of papers that share $l$ common topics, or to connect a cluster of $1$ topic and a cluster that share $l$ common topics.
        %In order to represent this notion in a generated network,
        %first, we randomly pick $n_{l}$ indices from the set $\Omega_{n_{l}} = \{1,2,\dots,n\} \setminus \Omega_{S^*}$, where $\Omega_{S^*}$ denotes a set of indices of papers for formulating $|S^*|$ ad-hoc links.
        %Next, $\forall j \in \Omega_{n_{l}}$, fill in arbitrary $l$ positions of $f_j^*$ with $1$s.

     \item \textbf{Third scenario.} In this scenario, we want to study a role of $\alpha^*$ in the network.
        In the first and second scenarios, we set $\alpha^* \sim \text{Unif}[-11,-10]$, so that it has little effect on creating random edges in the network.
        In the third scenario, we set $\alpha^* \sim \text{Unif}[-4,-3]$, whereas other parametric settings for $D^*, F^*$ and $S^*$ are same with those from the first and second scenarios.
        This setting has an effect on increasing the number of edges connecting the clusters of papers with $l$ topics and those with $1$ topic.
\end{itemize}

@@

\begin{enumerate}
    \item In the first scenario, we consider following three cases: $\{(n^{(i)},n_{1}^{(i)},K^{(i)},|S^*|^{(i)})\}_{i=1}^{3}$ $=\{(30,30,3,9), (80,80,4,18),$ $(120,120,5,30)\}$.
        If we take an example, the notation  $(n^{(1)},n_{1}^{(1)},K^{(1)},|S^*|^{(1)})=(30,30,3,9)$ means that we generate a network with $30$ papers. There are $3$ topics embedded in the network, and $9$ random ad-hoc links connect $3$ clusters of papers, where each cluster represents a collection of papers with same topic.
        Note that every paper in three networks, which are considered in this scenario, studies only about $1$ topic among $K$ topics.
    \item In the second scenario, we consider three cases where we have
        $\{(n^{(i)},n_{2}^{(i)},n_{3}^{(i)},K^{(i)},|S^{*}|^{(i)})\}_{i=1}^{3}=
        \{(120,0,10,3,18),$ $(210,50,0,3,18),(210,10,10,3,18)\}$.
        For instance, in the third case, we have a network with $210$ papers in total. There are $3$ topics commonly shared across the network.
        Among $210$ papers, $10$ papers randomly share $2$ topics out of $3$, other $10$ papers have $3$ mixed topics, whereas remaining $190$ papers only discuss $1$ topic.
        Note that the $3$ clusters from these $190$ papers are connected through $18$ random ad-hoc links.
    \item In the third scenario, we basically study the same $3$ cases with those from the second scenario.
        (i.e., $\{(n^{(i)},n_{2}^{(i)},n_{3}^{(i)},K^{(i)},|S^{*}|^{(i)})
        \}_{i=1}^{3}=\{(120,0,10,3,18), (210,50,0,3,18),(210,10,10,3,18)\}$)
        The only difference between these two scenarios comes from the random setting of $\alpha^*$. (i.e.,$\alpha^* \sim \text{Unif}[-4,-3]$)
\end{enumerate}

All $9$ networks that are elaborated in scenarios $1$, $2$ and $3$ are visualized in Fig\ref{fig:figure1}.
Note that ad-hoc links, which connect clusters of papers with $1$ topic, are colored in green.
Readers can refer the R code provided in $\dots$, for more detailed descriptions on parametric settings for generating networks in Fig\ref{fig:figure1}.

@@

\subsubsection{Choosing the tuning parameters and evaluation criteria}
We observe that choosing a good pair of tuning parameters is an important yet challenging issue in our setting.
Here we present a heuristic procedure for choosing a good pair of tuning parameters $(\gamma,\delta)$.
Following the scree-plot approach in Ji and Jin \cite{ji2016coauthorship}, we plot the largest $20$ eigenvalues of the adjacency matrix $X$, and find an ``elbow'' point where the eigenvalues seem to level off.
An index of the point, which is to the left of this elbow point, is considered as the number of the topics embedded in the network.
(We will denote this number as $\hat{K}^{\text{Scree}}$.)
We want to note the readers that the scree-plot analysis serves as a good guideline for determining the range of grids to search over.
With the estimate of the number of topics in the network in mind, we record the $\text{rank}(\widehat{L}^{\gamma,\delta})$ and $|\widehat{S}^{\gamma,\delta}|$ for each tuning parameter pair on a given grid.
We need to go through several iterations of this recording procedure to find a proper range of grid, in which we can get $\text{rank}(\widehat{L}^{\gamma,\delta})=\hat{K}^{\text{Scree}}$
and $10^{-4}|X| \leq |\widehat{S}^{\gamma,\delta}| \leq 10^{-1}|X|$, via adjusting the range of grid for $\gamma$ and $\delta$ repeatedly.
Once we find a grid, which satisfies above constraints, we choose a pair of tuning parameters: %($\gamma^{\text{Heu}},\delta^{\text{Heu}}$):
\[
    (\gamma^{\text{Heu}},\delta^{\text{Heu}}):=
    \big\{(\gamma,\delta): \text{rank}(\widehat{L}^{\gamma,\delta})=\hat{K}^{\text{Scree}},
    \quad \mbox{mode} |\widehat{S}^{\gamma,\delta}| \quad
    \text{s.t.} \quad 10^{-4}|X| \leq |\widehat{S}^{\gamma,\delta}| \leq 0.05|X| \big\}
\]
One might wonder how traditional model selection methods, such as the Bayes Information Criterion (BIC;\cite{schwarz1978estimating}) and the AIC, work where we recall that BIC and AIC are defined as follows:
\[
\mbox{BIC}(M) = -2  \mathbb{L}_n( \hat{\beta}(M)) + |M| \log \bigg(\frac{n(n-1)}{2}\bigg),
\]
and
\[
\mbox{AIC}(M) = -2  \mathbb{L}_n( \hat{\beta}(M)) + 2|M|.
\]
Here $M$ indicates the current model, which is implicitly understood that the model is obtained from certain tuning parameter pair $(\gamma,\delta)$.
We use $\mathbb{L}_n( \hat{\beta}(M))$ to denote the maximal log-likelihood for a given model $M$,
and $|M|$ is the number of free parameters in $M$, which is determined by the number of non-zeros in $\widehat{S}^{\gamma,\delta}$ and the low-rank matrix $\widehat{L}^{\gamma,\delta}$.
In detail, if we have $\text{rank}(\widehat{L}^{\gamma,\delta})=K$, we can establish the following
\[
|M| = \sum_{i < j}1_{\{S_{ij} \neq 0\}} + n K - \frac{K(K-1)}{2} + 1 ;
\]
since the number of free parameters in $\widehat{L}^{\gamma,\delta}$ is $K$ plus $nK - K(K+1)/2$, which is the number of free parameters in determining $K$ orth-normal vectors.
Additional $1$ in the last term is due to $\hat{\alpha}$.
We want to find a pair $(\gamma,\delta)$, which minimizes BIC($M$) and AIC($M$) as a function of $(\gamma,\delta)$ respectively, where we denote them as follows:
\[
    (\gamma^{BIC},\delta^{BIC}):= \mbox{arg min}_{\gamma, \delta}
    \mbox{BIC}(M),
    \quad
    (\gamma^{AIC},\delta^{AIC}):= \mbox{arg min}_{\gamma, \delta}
    \mbox{AIC}(M)
\]
We evaluate the models that are selected via our heuristic approach, BIC, and AIC by using following three evaluation metrics.

\begin{figure}[htbp]
\includegraphics[width=1\textwidth]{Fig2.pdf}
\caption{ Scree plots for $9$ synthetic Networks.
    $\hat{K}^{\text{Scree}}$ recovers the number of topics in network correctly for all $9$ cases.}
\label{fig:figure2}
\end{figure}

@@

\subsubsection{Several Observations}
%Given a network data $X$, after fitting the model with a proper pair of tuning parameters, $(\gamma,\delta)$, we need to determine whether node $i$ belongs to $k$th topic or not.
%We apply a simple $k$-means clustering on the fitted $L$ matrix's $K$ eigenvectors.
%For the illustration of performance of our fitted model after applying $k$-means algorithm on three synthetic scenarios, in Fig\ref{fig:figure1}, we plot the coordinates of each rows of first two eigen-vectors on $2$D plane.
%Furthermore, we find one interesting phenomenon.
%Coordinates of each rows from first two eigenvectors of estimated $\widehat{L}$ matrix in our model characterize the clustering behavior of embedded topics reasonably well.
%Our experience shows that with only first two eigenvectors of $\widehat{L}$, we can also cluster the nodes comparably well.
\begin{enumerate}
    \item \textbf{Model Selection.}
    First and foremost, choosing a good pair of tuning parameters is of essential issue when it comes to making a good statistical inference on data.
    As presented in Table\ref{tab:table1}, we observe that the traditional model selection methods, both BIC and AIC, perform poorly on choosing true models, whereas our heuristic approach chooses good models reasonably well for the 9 artificial cases.
    In the heuristic approach, scree-plot plays an important role when it comes to recovering the number of topics for all $9$ cases. (See Fig\ref{fig:figure2})
    On the other hand, both BIC and AIC choose the most parsimonious model with the smallest $K(=\text{rank}(\widehat{L}))$ and the smallest cardinality$(=|\widehat{S}|)$ of ad-hoc links among the estimated ($\widehat{L}$,$\widehat{S}$)s' over the given grid.

    \item \textbf{Node Membership.}
    After fitting the model with a proper pair of tuning parameters, $(\gamma,\delta)$, we need to determine whether the $i$th paper belongs to $k$th topic or not.
    We apply a simple $k$-means clustering algorithm on the $\widehat{L}$ matrix’s $K(=\text{rank}(\widehat{L}))$ eigenvectors.
    (We will denote column-wise concatenation of these $K$ eigenvectors as $\widehat{E}_{K} \in \mathbb{R}^{n\times K}$.)
    For $3$ cases in Scenario $1$, where each paper in the network can only have $1$ topic, we confirm that $k$-means algorithm performs well on classifying papers in the network.
    However, in Scenario $2$ and $3$ where we allow the papers in the network can have more than $1$ topic, naive implementation of $k$-means algorithm entails a problem, since it is not able to afford the overlapped membership of nodes.
    In order to obtain a sense on how many clusters of papers exist in latent space, we project each row of the $\widehat{E}_{K}$ on the first and second principal components of data matrix $\widehat{E}_{K}$, and plot the projected points on $2$-dimensional plane.
    We count the number of distinct clusters plotted on the plane. Subsequently, we run the $k$-means algorithm on the projected points.
    See Fig\ref{fig:figure3} for the references on how this procedure performs on $9$ synthetic cases.

    \item \textbf{Scenario $2$ vs. Scenario $3$.}
    We empirically observe that the number of edges between clusters $\big\{ C_{i,j}:\forall 1 \leq i \neq j \leq K \big\}$ and $\big\{ C_{i}: \forall 1 \leq i \leq K \big\}$ has an effect on their clustering behaviors in latent space. Here $C_{i}$ is used to represent a set of papers on $i$th topic, and $C_{i,j}$ is used to denote a collection of papers that have $i$th and $j$th topics.
    If we take a look at Fig\ref{fig:figure3}, Case $4$ in second scenario illustrates that it is difficult for us to visually distinguish the papers in $C_{1,2,3}$ and those in $\big\{ C_{i}: \forall 1 \leq i \leq 3 \big\}$ in projected space, whereas they are obviously distinguishable in Case $7$.
    Unfortunately, we can observe similar phenomenon in Case $5$ and $6$, where the exact separations of clusters $\big\{ C_{i,j}:\forall 1 \leq i \neq j \leq 3 \big\}$ are not made.
    %makes $k$-means algorithm difficult to distinguish the clusters of papers $C_{1,2}, C_{2,3}, C_{1,3}$ and $C_{1,2,3}$ from each other both in Case $5$ and $6$.
    On the other hand, in third scenario, distinct separations are made between $6$ clusters $C_{1}, C_{2}, C_{3}, C_{1,2}, C_{2,3}, C_{1,3}$ in Case $8$, and between $7$ clusters $C_{1}, C_{2}, C_{3}, C_{1,2}, C_{2,3}, C_{1,3}, C_{1,2,3}$ in Case $9$, so that we can explicitly know the membership of each paper in the network.

    % In fact, this observation is especially helpful for us to understand the behavior of our model with the statisticians’ citation network data, which we are going to explore in the following subsection.
    % In the statisticians’ citation network, we also observe clusters of papers, which have more than $1$ topic, behave similarly with those from the second scenario.

    \item \textbf{Ad-hoc links.}
    In our setting, ad-hoc links of synthetic network data are considered as ``across edges'' between clusters $\big\{ C_{i}: \forall 1 \leq i \leq K \big\}$.
    Our heuristic method works much better than either AIC or BIC in recovering the ad-hoc edges for the $6$ cases in $3$ scenarios.
    For the three Cases (i.e., Case $2,3,9$) where both AIC and BIC work well, all the pairs of tuning parameters in the grid give the same $|\widehat{S}^{\gamma,\delta}|$.

    %Since indices of non-zero entries of $S^{*}$ are randomly chosen, there might be some indices of positive $S^{*}_{ij}$ entries where $L^{*}_{ij}$ is also positive.
    %In this case, this makes the edges indistinguishable if they come from $S^{*}_{ij}$ or $L^{*}_{ij}$.
    %Some of ``across edges" are also attributed to $\alpha^{*}$, and unfortunately, our algorithm cannot make a difference whether the edge comes from $\alpha^{*}$ or $S^{*}_{ij}$.
    %So the total number of ``across edges'' might not be exactly same as $|S^*|$ as we set in our data generation setting.
\end{enumerate}

@@

\centering
\begin{tabular}{c|ccc|ccc|ccc}
            & \multicolumn{9}{c}{\textbf{Scenario 1}}                                              \\
            \cline{2-10}
            & \multicolumn{3}{c|}{Case 1} & \multicolumn{3}{c|}{Case 2} & \multicolumn{3}{c}{Case 3} \\
            \cline{2-10}
            & Heuristic   & AIC   & BIC  & Heuristic   & AIC   & BIC  & Heuristic   & AIC   & BIC  \\
            \hline
$M_{1}$   &    1(3)  &    0(2)   &  0(2)  &    1(4)    &  0(3)   &  0(3)  &    1(5)  &   0(4)    &   0(4) \\
$M_{2}$   &    1     &    0 &      0 &         1    &     1  &    1  &         1    &    1   &   1   \\
$M_{3}$   &    0     &    0 &      0 &         0    &     0  &    0  &         0    &    0   &   0   \\
%Grid Region &    &       &      &             &       &      &             &       &      \\
            \hline
\end{tabular}

\begin{tabular}{c|ccc|ccc|ccc}
            & \multicolumn{9}{c}{\textbf{Scenario 2}}                                              \\
            \cline{2-10}
            & \multicolumn{3}{c|}{Case 4} & \multicolumn{3}{c|}{Case 5} & \multicolumn{3}{c}{Case 6} \\
            \cline{2-10}
            & Heuristic   & AIC   & BIC  &    Heuristic   & AIC   & BIC  & Heuristic   & AIC   & BIC  \\
            \hline
$M_{1}$   &   1(3)     &     1(3)  &  1(3)    &      1(3)   &   1(3)    &  1(3)    &   1(3)     &  1(3)     &   1(3)   \\
$M_{2}$   &   $\frac{17}{18}$   &   0    &    0  &   $\frac{17}{18}$     &   0    &  0    &  $\frac{16}{18}$    &   0    &  0    \\
$M_{3}$   &   0 &     0  &   0   &        0     &    0   &  0    &        0     &   0    & 0 \\
%Grid Region &             &       &      &             &       &      &             &       &      \\
            \hline
\end{tabular}

\begin{tabular}{c|ccc|ccc|ccc}
            & \multicolumn{9}{c}{\textbf{Scenario 3}}                                              \\
            \cline{2-10}
            & \multicolumn{3}{c|}{Case 7} & \multicolumn{3}{c|}{Case 8} & \multicolumn{3}{c}{Case 9} \\
            \cline{2-10}
            & Heuristic   & AIC   & BIC  & Heuristic   & AIC   & BIC  & Heuristic   & AIC   & BIC  \\
            \hline
$M_{1}$  &    1(3)   &   1(3)    &  1(3)    &     1(3)        &    1(3)   &  1(3)    &   1(3)          &  1(3)      &  1(3)     \\
$M_{2}$  &     1       &   0  &    0  &    $\frac{15}{18}$         &   0  &  0  &   1   &  1    &   1     \\
$M_{3}$  &  $\frac{1}{7122}$  &  0  &  0   &   $\frac{3}{21927}$ &     0  &  0     &  $\frac{4}{21927}$ & $\frac{4}{21927}$ & $\frac{4}{21927}$ \\
%Grid Region &             &       &      &             &       &      &             &       &      \\
\end{tabular}
\caption{ For three scenarios, our heuristic method chooses the model with $\widehat{L}$ with true rank, $\widehat{S}$ whose $M_2$ value is close to $1$, and $M_3$ value is close to $0$.
A number in the parentheses represents the rank of $\widehat{L}$ estimated from ($\gamma^{\text{Heu}},\delta^{\text{Heu}}$), ($\gamma^{\text{AIC}},\delta^{\text{AIC}}$) and ($\gamma^{\text{BIC}},\delta^{\text{BIC}}$) for each case.}
\label{tab:table1}
\end{table}

\begin{figure}[htbp]
\includegraphics[width=1\textwidth]{Fig3.pdf}
\caption{ Plots of the projected points on the first (X-axis) and second (Y-axis) principal component of the data matrix $\widehat{E}_{K}$. Different colors represent different clusters of papers that $k$-means algorithm assigns.}
\label{fig:figure3}
\end{figure}

@@

\noindent These two topics are classical research topics in field of statistics.
First group talks about Variable Selection in high-dimensional data.
Majority of papers in second community study about Controlling False Discovery Rate in various statistical settings.
As expected, third group is quite hard to interpret and seems to have substructures.
For further investigation on this group, after obtaining the sub-network which is comprised only with the papers in the third group, we performed same analysis once again under the assumption that $K=4$ (See Fig$\ref{fig:figure3}$,right).
We obtain four sub-communities as follows:
